### 2018-11-30 manuscript/manuscript.rmd
first overlap figure

>>>>

matrix_overlap_rectangles = 
	lapply(sequence_matrices, function(x) lapply(sequence_matrices, function(y) overlap_rects(x,y))) %>% 
	unlist(recursive=FALSE) %>% 
	bind_rows()

ggplot(data=matrix_overlap_rectangles) + 
	scale_x_continuous(name="x") + 
	scale_y_continuous(name="y") +
	geom_rect( mapping=aes(xmin=xmin, xmax=xmax, ymin=ymin, ymax=ymax, fill=MSA ), alpha=0.5) + 
	facet_grid( matrix_1 ~ matrix_2 )
